Model Search in Relational Domains

### 2016-10-19 decision.tex
decision

\subsection{Decision}
A decision $\mathcal{D}$ is a meet irreducible that refines the 
current abstract valuation.  A decision can be of the form \pscmt{that's too restrictive?}
$\langle x R c \rangle$ or $\langle x R y \rangle$, where 
$R \in \{\preceq, \succeq\}$, $c$ is the bound and 
$\{x, y\}$ are program variables.  A decision must always 
be consistent with respect to the trail $\mathcal{T}$, that 
is, it must not contradict with the elements in the trail.

>>>>

\subsection{Decision}
A decision $\mathcal{D}$ is a meet irreducible that refines the 
current abstract valuation.  For example, a decision in interval 
domain can be of the form $\langle x R c \rangle$ where 
$R \in \{\leq, \geq\}$, $c$ is the bound.  A decision in 
relational domain such as octagon is of the form $ax - by \leq c$, 
where $x$ and $y$ are variables, $a,b \in \{-1,0,1\}$ are co-efficients, 
and $c \in \mathbb{R}\cup\{\infty\}$ is the bound of the inequality.    
A decision must always be consistent with respect to the trail 
$\mathcal{T}$, that is, it must not contradict with the elements 
in the trail.
